ITS_LIVE: A Cloud-Native Approach to Monitoring Glaciers from Space

### 2023-10-30 paper.qmd
fixing JPL affiliation

---
title: "ITS_LIVE: A Cloud-Native Approach to Monitoring Glaciers from Space"
author:
  - name: Luis A. López
    email: luis.lopezespinosa@colorado.edu
    affiliations: 
        - id: NSIDC
          name: NSIDC
          department: University of Colorado Boulder
  - name: Alex S. Gardner
    orcid: 0000-0002-8394-8889
    email: alex.s.gardner@jpl.nasa.gov
    affiliations:
        - id: NASA
          name: NASA
          department: Jet Propulsion Laboratory
  - name: Chad A. Greene
    email: chad.a.greene@jpl.nasa.gov
    orcid: 0000-0001-6710-6297
    affiliations:
        - id: NASA
          name: NASA
          department: Jet Propulsion Laboratory
  - name: Mark Fahnestock
    email: mfahnestock@alaska.edu
    affiliations:
        - id: UAF
          name: UAF 
          department: Geophysical Institute
  - name: Joseph H. Kennedy
    email: jhkennedy@alaska.edu
    affiliations:
        - id: UAF
          name: UAF
          department: Alaska Satellite Facility
  - name: Maria Liukis
    email: maria.liukis@jpl.nasa.gov
    affiliations:
        - id: NASA
          name: NASA
          department: Jet Propulsion Laboratory
  - name:  Theodore A Scambos
    email: tascambos@Colorado.EDU
    affiliations:
        - id: CIRES
          name: CIRES
          department: Earth Science and Observation Center
  - name:  Jacob R. Fahnestock
    email: jrfz31@gmail.com
    affiliations:
        - id: Wentworth Institute of Technology
          name: Wentworth Institute of Technology
abstract: |
  NASA's ITS_LIVE project delivers near-real-time information on global glacier dynamics and provides historical context for climate change with a record of how every glacier in the world has evolved over decades of satellite observation. To handle petabytes of data in the satellite archives and a constant influx of new observations, ITS_LIVE has adopted a modern cloud-native approach that is scalable, highly performant, user friendly, and embraces transparent and collaborative code development. As every discipline of Earth science is being transformed by a new era of remote sensing and cloud computing, ITS_LIVE offers a progressive approach to maximizing scientific advancements through open science.
keywords: 
  - glaciology
  - climate change
  - big data
  - cloud computing
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: IEEE VizCorner
      formatting: preprint
      model: 3p
      layout: twocolumn
      cite-style: super
---

@@

* The ITS_LIVE user community for their helpful  feedback.
* Pangeo community.
* Copernicus Sentinel data processed by ESA.
* Landsat data courtesy of the U.S. Geological Survey.
* Funding for ITS_LIVE provided by the NASA MEaSUREs program.

>>>>

---
title: "ITS_LIVE: A Cloud-Native Approach to Monitoring Glaciers from Space"
author:
  - name: Luis A. López
    email: luis.lopezespinosa@colorado.edu
    affiliations: 
        - id: NSIDC
          name: NSIDC
          department: University of Colorado Boulder
  - name: Alex S. Gardner
    orcid: 0000-0002-8394-8889
    email: alex.s.gardner@jpl.nasa.gov
    affiliations:
        - id: NASA
          name: NASA
          department: Jet Propulsion Laboratory, California Institute of Technology
  - name: Chad A. Greene
    email: chad.a.greene@jpl.nasa.gov
    orcid: 0000-0001-6710-6297
    affiliations:
        - id: NASA
          name: NASA
          department: Jet Propulsion Laboratory, California Institute of Technology
  - name: Mark Fahnestock
    email: mfahnestock@alaska.edu
    affiliations:
        - id: UAF
          name: UAF 
          department: Geophysical Institute
  - name: Joseph H. Kennedy
    email: jhkennedy@alaska.edu
    affiliations:
        - id: UAF
          name: UAF
          department: Alaska Satellite Facility
  - name: Maria Liukis
    email: maria.liukis@jpl.nasa.gov
    affiliations:
        - id: NASA
          name: NASA
          department: Jet Propulsion Laboratory, California Institute of Technology
  - name:  Theodore A Scambos
    email: tascambos@Colorado.EDU
    affiliations:
        - id: CIRES
          name: CIRES
          department: Earth Science and Observation Center
  - name:  Jacob R. Fahnestock
    email: jrfz31@gmail.com
    affiliations:
        - id: Wentworth Institute of Technology
          name: Wentworth Institute of Technology
abstract: |
  NASA's ITS_LIVE project delivers near-real-time information on global glacier dynamics and provides historical context for climate change with a record of how every glacier in the world has evolved over decades of satellite observation. To handle petabytes of data in the satellite archives and a constant influx of new observations, ITS_LIVE has adopted a modern cloud-native approach that is scalable, highly performant, user friendly, and embraces transparent and collaborative code development. As every discipline of Earth science is being transformed by a new era of remote sensing and cloud computing, ITS_LIVE offers a progressive approach to maximizing scientific advancements through open science.
keywords: 
  - glaciology
  - climate change
  - big data
  - cloud computing
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: IEEE VizCorner
      formatting: preprint
      model: 3p
      layout: twocolumn
      cite-style: super
---

@@

* The ITS_LIVE user community for their helpful  feedback.
* Pangeo community.
* Copernicus Sentinel data processed by ESA.
* Landsat data courtesy of the U.S. Geological Survey.
* Funding for ITS_LIVE provided by the NASA MEaSUREs program.
* A portion of this work was conducted at the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration ©2023 All rights reserved.
